Supplementary Information

### 2021-06-11 doc/manuscript/ForestGEO_treerings_SI.Rmd
create year validation figure
closes #135

decadal_analysis_verification_example_legend <- "Figure S5. Example comparison of year effect in GLS model with independent decadal analysis: BCNM"

@@

>>>>

year_validation_legend <- "Figure S5. Example comparison of year effect in GLS model with independent decadal analysis: Harvard Forest"

@@

## `r year_validation_legend`

![](tables_figures/year_effect_validation.png)

`r year_validation_legend`. Panel (a) shows results the effect of year in the full GLS model (all significant with t-test’s p-value <0.05). Other terms in the model are held constant at their medians. Transparent ribbons indicate 95% confidence intervals. Panels (b-e) show relationships between DBH and BAI by decade for each species individually. These plots visualize the data included in the GLS model, separated by decade, using a probability density function. Transparent ribbons indicate 95% confidence intervals. Parallel plots for all sites are available in the GitHub repository for this project: https://github.com/EcoClimLab/ForestGEO-tree-rings/tree/master/doc/supplementary_figures/decadal_plots.
